---
title: "Alcohol vs Seat choice"
author: "Colton Beardsley"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

# Introduction

We will be looking into the DavisData data set that is included with tidyverse to see if there is and correlation between alcohol consumption and the chosen seat.  

$H_0$ There is no difference in the data between alcohol and seat.

$H_A$ There is difference in the data between alcohol and seat.

## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

```{r}
glimpse(davisdata)
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```


Looking at the data using glimpse we can see that Alcohol is a continuous numerical and seat is a regular categorical. This problem is a numerical categorical, because of that we will use the Numerical~Cat helper file in CandP. We will also use the mytricks to factor the categorical data using dyplr. We will show our graphical results using ggplot2, numerical with favstats, and run inferential tests with an anova because we have more than two categories and then a TukeyHSD to find where the differences are in our data.


### Graphical Descriptive Results

``` {r include = TRUE, echo = FALSE}
ggplot(data = davisdata, aes(x = Seat, y = alcohol) ) +
geom_boxplot (notch=FALSE,outlier.colour = "red",outlier.size = 2, fill = "darkgray") +
stat_boxplot (geom ='errorbar') +
labs (x = "Seat", y = "Alcohol Consumed", title = "Alcohol vs Seat Choice") +
theme (plot.title = element_text(hjust = 0.5, size = 16) )
```


## Numerical Summarys 



## Inferential Tests



## Conclusions



