---
title: "Alcohol vs Seat choice"
author: "Colton Beardsley"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

```{r}
glimpse(davisdata)
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```


Looking at the data using glimpse we can see that Alcohol is a continuous numerical and seat is a regular categorical. This problem is a numerical categorical, because of that we will use the Numerical~Cat helper file in CandP. We will also use the mytricks to factor the categorical data using dyplr. We will show our graphical results using ggplot2, numerical with favstats, and run inferential tests with an anova because we have more than two categories and then a TukeyHSD to find where the differences are in our data.


## Numerical Summarys 



## Inferential Tests



## Conclusions



